---
output: github_document
---


<!-- badges:start -->
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)
<!-- badges:end -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "When more is less: adding more traits dilutes the functional diversity-environment relationship"
```

# fd-dimensionality: Effect of the number of traits on fd-env relationships

This is the companion repository for the following paper:

> Grenié M., Munoz F., Violle C. (2021). _When more is less: adding more traits dilutes the functional diversity-environment relationship_. *Submitted*


### How to cite

Please cite this compendium as:

> Grenié M., Munoz F., Violle C., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>


### How to download or install

You can install this compendium as an R package, `fddimensionality`, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("Rekyt/fddimensionality_ms")
```


### How to run

The analyses of the compendium heavily rely on the use the of workflow management package [`drake`](https://cran.r-project.org/package=drake). All analyses are contained within the `R` directory.

To run them run the following lines:

```{r running-workflow, eval = FALSE}
# Beware this may take a long time (>10 hours)
pkgload::load_all()
drake::make(global_workflow())
```
